### 2015-07-04 thesis/thesis/chap2/chap2.tex
changes

@@

@@

>>>>

\subsection{Communities of Web Services}\label{sec:communities_rel}

@@

\subsection{Web Service Community Formation}\label{sec:communities_for_rel}

@@

\subsection{Coopetitive Behaviour Within Communities of Web Services}\label{sec:coopetetive}

At the best of our knowledge, there is no work in the literature
of service and agent computing addressing the issue of coopetition
strategies and when to cooperate or to compete. However, some
relevant proposals to the model presented in this paper are the
ones that address service selection and task allocation
mechanisms. In many frameworks proposed in the literature, service
selection and task allocation are regulated based on the
reputation parameter \cite{Bentahar,Rosario,Ruth,Yahyaoui}.
\textbf{In \cite{Huang}, the authors propose a framework to match potential
benefits of services while cooperating with one another. The
interesting idea is to consider the benefits under four
categories: innovation and learning, internal business process,
customer, and financial benefits.
Innovation and learning perspective} focuses on the knowledge, skills, and systems needed to improve the business continually. Necessary factors to build strategic capabilities and efficiency in addressed in internal business process. Values that customers seek are considered in \emph{customer perspective} and financial performance to maximize the shareholder value are analyzed in \emph{financial perspective}. Their goal is to design the framework for cooperating web services, inline with business strategy of firms in IT industry.
In \cite{Alchieri}, the authors
present a dependable framework for cooperative service agents that
is based on the tuple space coordination model. The
intrusion-tolerant perspective is emphasized in this paper where
several security mechanisms are developed to enable a reliable
coordination system. %In \cite{Maximilien2}, authors propose
%ontology for quality of service. Users compute the web services'
%reputation using ratings.
The proposed frameworks mostly aim to facilitate the coordination
mechanism between services. However, the opposite strategy of
competing is not analyzed where services might be more successful
when competing within the same group. In fact, services are not
always willing to cooperate even if they have some common goals,
particularly when they operate within groups such as communities.
In such a context, service agents can follow different interacting
strategies and have to decide when to compete and when to
cooperate so that their ultimate goal, maximizing their incomes,
can be better achieved. In our framework, we analyze those
different strategies to help services in their decision making
process when these
agents function within communities. %We summarize most of
%these proposals and concentrate on strategic decision making
%system that ranks web services in the community and analyze their
%effective interacting strategies to accomplish continuous
%requested tasks.
We enable service agents to reasonably evaluate and decide over
their coopetition strategies, which means deciding when to compete
and when to cooperate.

Furthermore, there are a number of related proposals that take
into account the correlation between (web) services and the ways
these services coordinate their actions to accomplish the required
tasks. In \cite{Jurca,Jurca2,Malik,Maximilien1,Yahyaoui}, the
authors propose to rank services based on their reputation in the
system and to use this ranking as a means to facilitate
cooperation of services. In those models, services rely on one
another on the basis of the reputation ranking system, using,
among other parameters, the QoS \cite{Qian-Tao-2012}. There are
other models that facilitate cooperation mechanisms among services
using various techniques. Examples of those techniques include 1)
coordination between two types of behaviors associated with
component services: operational and control behaviors
\cite{Yahyaoui3}; 2) Services-based workflows \cite{Wu-2011}; 3)
transaction-based approaches \cite{Gao,Rosario}; 4) agent
coordination mechanisms \cite{Charif,Gutierrez-Garcia-2013}; 5)
logical techniques \cite{Okutan,Tang}; and 6) community models,
which are virtual structures that aim at increasing the visibility
of services and facilitating their discovery and composition by
hosting and gathering services having similar or complementary
functionalities but different QoS parameters
\cite{Khosravifar2010}. %There are also some frameworks
%\cite{Ferguson,Ferguson2} that consider game-theoretic analysis on
%the expected payoffs obtained via different acting strategies.
However, deciding about which strategy to choose when services are
competing but still need to cooperate to accomplish complex tasks
has not been addressed and kept as open issue in all these
proposals as faithfully argued in
\cite{Maamar2011,Khosravifar-ICSOC2012}.
